Symmetric Circuits for Rank Gates

### 2017-07-26 sections/symmetric-circuits.25-07-2017.tex
26/07/2017

\documentclass[12pt]{report}

% This first part of the file is called the PREAMBLE. It includes
% customizations and command definitions. The preamble is everything
% between \documentclass and \begin{document}.

\usepackage[margin=1in]{geometry} % set the margins to 1in on all sides
\usepackage{graphicx} % to include figures
\usepackage{amsmath} % great math stuff
\usepackage{amsfonts} % for blackboard bold, etc
\usepackage{amsthm} % better theorem environments
\usepackage{xspace}

% various theorems, numbered by section

\newtheorem{thm}{Theorem} \newtheorem{claim}[thm]{Claim}
\newtheorem{remark}[thm]{Remark} \newtheorem{definition}[thm]{Definition}
\newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary} \newtheorem{conj}[thm]{Conjecture}

\DeclareMathOperator{\id}{id}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\nats}{\mathbb{N}}

\newcommand{\logic}[1]{\text{\upshape #1}\xspace}
\newcommand{\FPC}{\logic{FPC}}
\newcommand{\FO}{\logic{FO}}
\newcommand{\FP}{\logic{FP}}
\newcommand{\FPR}{\logic{FPrk}}
\newcommand{\CPTC}{\logic{$\tilde{\text C}$PT(Card)}}

\newcommand{\PT}{\ensuremath{\mathrm{P}}\xspace}

\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
\newcommand{\RR}{\mathbb{R}} % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}} % for Integers
\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
\newcommand{\stab}{\text{\textbf{Stab}}}
\newcommand{\setstab}{\text{\textbf{SetStab}}}
\newcommand{\matstab}{\text{\textbf{MatStab}}}
\newcommand{\inv}{\text{\textbf{inv}}}
\newcommand{\aut}{\text{\textbf{Aut}}}
\newcommand{\kernal}{\text{\textbf{ker}}}
\newcommand{\alt}{\text{\textbf{Alt}}}
\newcommand{\sym}{\text{\textbf{Sym}}}
\newcommand{\std}{\text{\textbf{std}}}
\newcommand{\rank}{\text{\textbf{rk}}}
\newcommand{\orb}{\text{\textbf{Orb}}}
\newcommand{\SP}{\text{\textbf{SP}}}
\newcommand{\SPs}{\text{\textbf{SPs}}}
\newcommand{\maj}{\text{\textbf{maj}}}
\newcommand{\dom}{\text{\textbf{Dom}}}
\newcommand{\img}{\text{\textbf{Img}}}
\newcommand{\child}{\text{child}}
\newcommand{\countgate}{\text{count}}
\newcommand{\agree}{\text{AGREE}}
\newcommand{\supp}{\text{SUPP}}
\newcommand{\rankparam}{\text{PARAM}}
\newcommand{\consp}{\text{sp}}
\newcommand{\consps}{\text{sps}}
\newcommand{\row}{\text{row}}
\newcommand{\column}{\text{col}}
\newcommand{\rowsp}{\text{r}}
\newcommand{\colsp}{\text{c}}
\newcommand{\EV}{\text{EV}}
\newcommand{\type}{\text{type}}
\newcommand{\types}{\text{types}}
\newcommand{\spstab}[1]{\stab (\consp (#1))}

\newcommand{\Alpha}{A}
\newcommand{\matsym}{\text{\textbf{MatSym}}}
\begin{document}

\title{Symmetric Circuits for Rank Gates}

\author{Anuj Dawar and Gregory Wilsenach \\ 
Computer Laboratory \\
University of Cambridge}

\maketitle

\tableofcontents

\chapter{Introduction}

A finite relational structure, such as a graph, can be represented as a binary
string in a standard way (for instance, by enumerating its adjacency matrix).
When we speak of the computational complexity of properties of graphs, we assume
such an encoding in order to present the structure as input to a machine or
circuit or other appropriate computational model. The properties of structures
we are interested in studying are invariant under isomorphisms. This requirement
translates into an invariance condition on sets of strings---say that a language
$L \subseteq \{0,1\}^\star$ is a \emph{graph property} if, whenever $x \in L$
for a string $x$ representing a graph $G$, we have $y\in L$ for any string $y$
obtained from $x$ by re-ordering the vertices of $G$. The central open question
in descriptive complexity---whether there is a logical characterisation of the
polynomial-time decidable properties of finite relational structures--- can then
be understood as the question of characterizing those languages $L$ that are in
$\PT$ and are graph properties.

Anderson and Dawar~\cite{AndersonD17} study this question through the lens of circuit
complexity, by considering \emph{symmetric circuits}. These are circuits that
necessarily accept graph properties, with this fact explicitly witnessed by
automorphisms of the circuit. To be precise, we can think of a property of
(directed) graphs on $n$ vertices as being given by a Boolean function $f:
\{0,1\}^{n^2} \rightarrow \{0,1\}$ which takes as input the $n^2$ potential
edges and outputs $1$ if the property is satisfied by the graph given on the
input. The function $f$ is \emph{graph-symmetric} in the sense that any permutation of
its inputs induced by a permutation of the $n$ vertices leaves $f$ unchanged
(note this is not the same thing as requiring that $f$ is invariant under all
permutations of its inputs). A symmetric circuit is a circuit computing a
Boolean function of $n^2$ inputs where each permutation of $[n]$ can be extended
to an automorphism of the circuit. Such a circuit necessarily computes an
invariant function.

The results of~\cite{AndersonD17} show a tight relationship between the decdability of
a graph property by means of a polynomial-size family of symmetric circuits and
its definability in extensions of fixed-point logic. In particular, they show
that a property is definable in fixed-point logic with counting ($\FPC$) if, and
only if, it is decidable by a polynomially-uniform family of symmetric circuits
using Boolean and majority gates (or, equivalently, threshold gates). Without
the symmetry restriction, polynomial-size families of circuits have the same
computational power whether we restrict ourselves to Boolean gates only or allow
richer bases such as threshold gates. One consequence of the results
in~\cite{AD14} is that, with the requirement of symmetry, these different bases
do yield different expressive power, suggesting some lack of robustness to the
model. One of the results in the present paper shows that the model with
majority circuits is robust in the sense that it is able to simulate, by means
of symmetric circuits, any symmetric circuit composed of gates computing Boolean
functions that are themselves symmetric (in the sense that they are invariant
under \emph{all} permutations of their inputs. Thus, any property decidable by a
polynomially-uniform family of such circuits is definable in $\FPC$.

This motivates the study of symmetric circuit families that involve gates which
themselves may compute non-symmetric functions. In particular, motivated by the
study of rank logic~\cite{DGHL09,GP15}, we consider gates that are
\emph{matrix-symmetric}. These are gates computing a Boolean function $f:
\{0,1\}^{A \times B} \rightarrow \{0,1\}$ which is invariant under arbitrary
permutations of $A$ and $B$. A typical example is the function computing the
rank of an $A \times B$ $0$-$1$ matrix. We show that the support theorem of
Anderson and Dawar can be shown to hold, even in the presence of
matrix-symmetric gates. This allows us to show that definability in the logic
fixed-point with rank ($\FPR$) is the same as decidability by
polynomially-uniform families of symmetric circuits with rank gates.

% Another extension of $\FPC$ that has received much attention in the descriptive
% complexity literature is the class $\CPTC$ of \emph{choiceless polynomial time
%   with counting}. The work of~\cite{AD14} leaves open the question of obtaining
% a circuit characterization of this class and it was suggested there that this
% would require a relaxation of the notion of symmetry used in defining symmetric
% circuits. In particular, while $\CPTC$ is based on a machine model designed to
% preserve symmetry by forbidding choices, the polynomial time and space
% restrictions apply int he context of the symmetries fo a \emph{single input
%   structure}. In this paper, we consider a relaxation of the notion of symmetric
% circuit intended to capture exactly this intuition. However, we are able to show
% that this does not yield a characterization of $\CPTC$. In particular, we show
% that no family in this class of relaxed symmetric circuits can distinguish odd
% from even Cai-F\"urer-Immerman graphs, something we know is do-able in
% $\CPTC$~\cite{DRR08}.

\chapter{Background}
In this section we present basic background on logics, first-order structures,
and symmetric circuits.

\section{Logic and Structures}
A \emph{relational vocabulary} (usually denoted by $\tau$) is a finite sequence
of relation symbols $R_1, \ldots, R_k$, such that for all $i \in [k]$, $R_i$ has
arity of $r_i \in \nats$.

A $\tau$-structure $\mathcal{A}$ is a tuple $\langle U, R^{\mathcal{A}}_1 ,
\ldots , R^{\mathcal{A}}_k \rangle$, where $U$ is a set and called the
\emph{universe} of $\mathcal{A}$ and for all $i \in [k]$ the relations
$R^{\mathcal{A}}_i \subseteq U^{r_i}$. The elements of $U$ are called the
elements of $\mathcal{A}$. A \emph{multi-sorted} structure is one whose universe
is a disjoint union, where each set in the union is called a \emph{sort}. The
size of a structure is the cardinality of its universe.

All structures in this paper are finite.

\section{First Order, Fixed-Point, Counting}

Let $\FO(\tau)$ denote \emph{first order logic} with respect to the vocabulary
$\tau$. \emph{Fixed-Point Logic} is the extension of $\FO(\tau)$ with an
inflationary fixed-point operator (see \cite{} for details). For logic
$\mathcal{L}$, a formula $\phi \in \mathcal{L}(\tau)$, $x$ a $k$-length tuple of
variables, $\mathcal{A}$ a (finite) structure, and $a \in U^k$, we have that
$\phi (x)$ denotes that the variables in $x$ are free in $\phi$ and we write
$\mathcal{A} \models_{\mathcal{L}} \phi[a]$ iff the the formula $\phi$ is true
in $\mathcal{A}$ with respect to $\mathcal{L}$ with the variables $x$ assigned
to $a$. The context usually makes the logic obvious, and in that case we usually
drop the subscript.

We also recall the definition of \emph{fixed-point logic with counting} $\FPC$,
an extension $\FP$ with counting quantifiers. For a structure $\mathcal{A}$,
Formulas of this logic are evaluated over a structure $\mathcal{A}$ by extending
that structure to $\mathcal{A}^\leq$, a two sorted extension of $\mathcal{A}$ by
an ordered number sort $\{1, \ldots, \vert U\vert \}$. Variables are taken to be
either point variables, ranging over $U$ or number variables ranging over
$[\vert U \vert]$. The counting quantifiers are of the form $\#_x$, where $x$ is
either a point or number variable and for $\phi(x) \in \FPC(\tau)$, $\#_x
\phi(x)$ is a term denoting the element of the number sort corresponding to
$\vert \{a \in \mathcal{A} | \mathcal{A} \models \phi[a]\}\vert$. Note
additionally that $k$-tuples of number variables can be used to encode numbers
in $\FPC$ of size up to $\vert U\vert^k$. For more details on $\FPC$ please see
\cite{}.

\section{Rank Logic}
This still needs to be filled in

\section{Symmetric Circuits}
This still needs to be filled in

\chapter{Symmetric Circuits}
In this section we discuss symmetric circuits, their limitations and extensions
of this model.

\section{Symmetric Circuits and Limitations}
Symmetric circuits, as developed by Anderson and Dawar, are, importantly defined
over (complete) Boolean basis consisting of symmetric functions. The following
result shows that once a majority gate has been included in this basis any
symmetric function can be computed using polynomial-size symmetric circuits, and
as such no additional symmetric function added to the Basis improves the power
of the model.

@@

\section{G-Symmetric Functions}
In order to extend the notion of a circuit by extending the basis we need to
consider functions that are not symmetric in the full sense of the term but have
some weakened notion of symmetry.

@@

\section{Symmetric Circuits with Matrix-Symmetric Gates}

@@

% In this section I discuss how to determine the rank a matrix labelling at some
% gate $g$. This is a rough copy written for the purpose of discussion. In this
% section we fix some circuit $C_n$ and some rank gate $g$ in $C_n$ with a set
% of children $H$ and matrix labelling $L: [a] \times [b] \rightarrow H$ (which
% we assume WLOG is a bijection).

\chapter{Symmetry and Support}
In order to analyse families of symmetric circuits we will need to develop some
theory for analysing symmetries. In this section we define the terms needed
(e.g. the notion of a support) and prove basic results. We then prove the first
important theorem in this paper, the support theorem, using these tools. It is
worth noting that we prove the support theorem for arbitrary symmetric circuits
with matrix-symmetric gates, not just for rank gates.

\section{Supports and Supporting Partitions}
In this section we formally define a support and the related notion of a
supporting partition.

\begin{definition}
  Let $G$ be a subgroup of $\sym_n$ and let $S \subseteq [n]$. Then $S$ is a
  \emph{support} for $G$ if $\stab(S) \subset G$.
\end{definition}

\begin{definition}
  Let $G$ be a subgroup of $\sym_n$ and $\mathcal{P}$ be a partition of $[n]$.
  Then $\mathcal{P}$ is a \emph{supporting partition} for $G$ if
  $\stab(\mathcal{P}) \subseteq [n]$.
\end{definition}

Notice that if $\mathcal{P}$ is a supporting partition for $G$ and $P \in
\mathcal{P}$ then $\stab([n] \setminus P) \subseteq \stab(\mathcal{P}) \subset
G$, i.e. $[n] \setminus P$ is a support for $G$.

These supporting partitions admits a natural partial order in terms of
coarseness. If $\mathcal{P}, \mathcal{P}'$ we say that $\mathcal{P}'$ is as
course as $\mathcal{P}$ (denoted by $\mathcal{P}' \supseteq \mathcal{P}$) if for
all $x \in \mathcal{P}$ there exists $y \in \mathcal{P}'$ such that $x \subseteq
y$ \cite{AndersonD17}.

Anderson and Dawar \cite{AndersonD17} show that for any permutation group $G
\subseteq \sym_n$ a unique coarsest partition can always be found. We call this
partition the \emph{canonical supporting partition}, and denote it by $\SP (G)$.
This canonical supporting partition, along with the above observation about
supports, will allow us to construct for each group a canonical support.

\begin{definition}
  Let $G$ be a subgroup of $\sym_n$. Let $\| SP(G) \| = \min \{\vert [n]
  \setminus P \vert : P \in SP(G) \}$. We say that $G$ has small support if $\|
  SP(G) \| < \frac{n}{2}$.
\end{definition}

\begin{definition}
  Let $G$ be a subgroup of $\sym_n$ such that $G$ has small support. Let
  $\consp(G) = [n] \setminus P$, where $P$ is the maximal element of $\SP(G)$.
  We call $\consp(G)$ the canonical support of $G$.
\end{definition}

\begin{remark}
  Include a remark about the importance of asserting the size consideration. Use
  the alternating group as an example.
\end{remark}

We state the following two results from Anderson and Dawar \cite{AndersonD17}.

\begin{lem}
  \label{lem:SP_conjugation}
  Let $G \leq \sym_n$ and $\sigma \in \sym_n$ then $\sigma \SP (G) = \SP(\sigma
  G \sigma^{-1})$.
\end{lem}

\begin{lem}
  For any $G \leq \sym_n$ we have that $\stab (\SP (G)) \subseteq G
  \setstab(\SP(G))$.
\end{lem}

\section{Group Action on Supports}
In this paper, distinct the case of Anderson and Dawar \cite{AndersonD17}, we
will need to develop theory and terminology for dealing with group actions (and
supports) on more than just gates in the circuit. In particular, we use this
theory for understanding the actions on the rows and columns of a labelling of a
gate.

\begin{definition}
  Let $G$ be a subgroup of $\sym_n$ and $X$ be a set on which a left group
  action of $G$ on $X$ is defined. We denote the canonical supporting partition
  of $x\in X$ by $\SP (x) = \SP (\stab(x))$. We say that $x \in X$ has small
  support if $\stab(x)$ has small support. We say that $X$ has small supports if
  all $x \in X$, $x$ have small support.

  If $x \in X$ has small support, we denote the \emph{canonical support} of $x$
  by $\consp(x) = \consp (stab(x))$.
\end{definition}

\begin{definition}
  Let $G$ be a group and $X$ be a set on which a left group action of $G$ on $X$
  is defined. Then $\stab_G (x) = \{\pi \in G : \pi x = x\}$ and $\orb_G (x) =
  \{\pi x : \pi \in G\}$. In the event that the context makes the group obvious
  we omit the subscript.
\end{definition}

\begin{lem}
  \label{lem:stab_conjugation}
  Let $G$ be a subgroup of $\sym_n$, $X$ be a set on which a left group action
  of $G$ on $X$ is defined and $\sigma \in G$. Then for any $x \in X$ it follows
  that $\sigma \stab (x) \sigma^{-1} = \stab(\sigma x)$.
\end{lem}

\begin{proof}
  Let $\pi \in \stab(x)$, then $\sigma \pi \sigma^{-1}(\sigma x) = \sigma \pi
  (x) = \sigma (x)$, and so $\sigma \pi \sigma^{-1} \in \stab(\sigma x)$. Let
  $\pi \in \stab(\sigma (x))$ then $\pi \sigma (x) = \sigma (x)$ and so
  $\sigma^{-1} \pi \sigma (x) = x$. It follows that $\sigma^{-1} \pi \sigma \in
  \stab(x)$ and so $\pi = \sigma (\sigma^{-1} \pi \sigma) \sigma ^{-1} \in
  \sigma \stab(x) \sigma^{-1}$.
\end{proof}

\begin{lem}
  \label{lem:support_mapping}
  Let $G $ be a subgroup of $\sym_n$, $X$ be a set on which a left group action
  of $G$ on $X$ is defined and $\sigma \in G$. Then for any $x \in X$ it follows
  that $\sigma \SP (x) = \SP (\sigma x)$ and, if $x$ has small support, $\sigma
  \consp (x) = \consp (\sigma x)$.
\end{lem}
\begin{proof}
  From Lemma \ref{lem:SP_conjugation} and Lemma \ref{lem:stab_conjugation} have
  that $\sigma \SP (x) = \SP(\sigma \stab(h) \sigma^{-1}) = \SP (\stab(\sigma
  x)) = \SP (\sigma x)$. Thus proving the first part of the statement.

  From the fact that $\| \SP(x) \| < \frac{n}{2}$ it follows there exists a
  unique $P_1 \in \SP(x)$ such that $\vert P_1 \vert > \frac{n}{2}$ and
  $\consp(x) = [n] \setminus P_1$. But then $\sigma \consp (x) = \sigma([n]
  \setminus P_1) = [n] \setminus (\sigma P_1)$. We note that $\sigma P_1 \in
  \sigma \SP (x) = \SP(\sigma x)$ and $\vert \sigma P_1 \vert > \frac{n}{2}$.
  Thus $\sigma P_1$ is the unique largest partition in $\SP(\sigma x)$, and so
  $\consp(\sigma x) = [n]\setminus (\sigma P_1) = \sigma (consp(x))$. Thus
  proving the second part of the statement.
\end{proof}

\begin{lem}
  Let $G$ be a subgroup of $\sym_n$, $X$ be a set on which a left group action
  of $G$ on $X$ is defined. Then for any $x \in X$ with small support, and
  $\sigma, \sigma' \in G$ such that $\sigma (vec{\consp}(x)) = \sigma'
  (\vec{\consp}((x))$ we have that $\sigma (x) = \sigma'(x)$.
\end{lem}
\begin{proof}
  We have that $(\sigma')^{-1}\sigma(\vec{\consp}(x)) = \vec{\consp}(x)$ and so
  $(\sigma')^{-1} \sigma (x) = x$ and thus $\sigma (x) = \sigma' (x)$.
\end{proof}

% \begin{lem}
%   Let $G \leq \sym_n$, $X$ be a set on which a left group action of $G$ on $X$
%   is defined and $\sigma \in G$. Then if $y \in \orb_{G} (x)$ and $\consp (x)
%   = \consp (y)$ then $x = y$.
% \end{lem}

% \begin{proof}
%   Let $\sigma \in G$ be such that $\sigma x = y$. Then $\consp(x) = \consp (y)
%   = \consp (\sigma x) = \sigma \consp (x)$. Thus $\sigma (\sp (x))$
% \end{proof}

% \begin{definition}
%   Let $h \in H$. Let $\stab_r(h)$ be a subgroup of $\stab(\consp(g))$
%   consisting of exactly those permutations $\sigma$ such that $\row (\sigma h)
%   = \row (h)$. Let $\stab_c(h)$ be a subgroup of $\stab(\consp(g))$ consisting
%   of exactly those permutations $\sigma$ such that $\column (\sigma h) =
%   \column(h)$.
% \end{definition}

% \begin{definition}
%   A set $S \subseteq [n]$ is called a row-support for $h$ if $S$ is a support
%   for $\stab_r(h)$. A set $S \subseteq [n]$ is called a column-support for $h$
%   iff $S$ is a support for $\stab_c(h)$.
% \end{definition}

% \begin{definition}
%   A partition $\mathcal{P}_r$ is called a row-supporting partition iff
%   $\mathcal{P}_r$ is a support for $\stab_r(h)$. A partition $\mathcal{P}_c$
%   is called a column-supporting partition iff $\mathcal{P}_c$ is a support for
%   $\stab_c(h)$.
% \end{definition}

% \begin{definition}
%   Let $\SP^r(h)$ denote the conical supporting partition and $r_h$ the
%   canonical support of $\stab_r(h)$. Similarly, let $\SP^c(h)$ denote the
%   conical supporting partition and $c_h$ the canonical support of
%   $\stab_c(h)$.
% \end{definition}

% \begin{definition}
%   Let $G \subseteq \sym_n$ be a subgroup. Then let $\SPs(G)$ be the set of all
%   supporting partitions of $G$ and $\consps(G)$ be the set of all supports of
%   $G$.
% \end{definition}

% We now prove a few important lemmas on supports.

% \begin{lem}
%   Let $A, B \leq \sym_n$ then $\SP(A \cap B) \subseteq \SP (A) $.
% \end{lem}
% \begin{proof}
%   Let $\mathcal{P}$ be a supporting partition of $A \cap B$. Then
%   $\mathcal{P}$ is a supporting partition of $A$. Since $\SP(A)$ is coarser
%   than all such partitions the result follows.
% \end{proof}

% \begin{lem}
%   Let $h \in H$, then $\SP(\stab(h)) \subseteq \SP (\stab (\row (h)))$ and
%   $\SP (\stab(h)) \subseteq \SP (\stab (\column(h)))$.
% \end{lem}
% \begin{proof}
%   It can be shown that $\stab (h)$
% \end{proof}

% The following lemma will be used to prove the relationship between the support
% of a gate and the supports of its row and columns.
% % Use this lemma + a support type theorem in order to get the result.
% \begin{lem}
%   Let $G \leq \sym_n$, $X_1$ and $X_2$ be sets on which left group actions of
%   $G$ on $X_1$ and $X_2$ are defined. Let $x_1 \in X_1$ and $x_2 \in X_2$ and
%   suppose $\vert \consp(x_1) \vert < \frac{n}{2}$ and $ \vert \consp(x_2)
%   \vert < \frac{n}{2}$. Then if $\SP(\stab(x_1)) \subseteq \SP (\stab(x_2))$
%   then $\consp (x_2) \subseteq \consp (x_1)$.
% \end{lem}
% \begin{proof}
%   Since $\vert \consp(x_1) \vert = \| \SP (\stab(x_1)) \| < \frac{n}{2}$ it
%   follows that there a unique maximal $P_1 \in \SP (\stab(x_1))$ such that
%   $\vert P_1 \vert > \frac{n}{2}$. Similarly there is a unique maximal $P_2
%   \in \SP (\stab(x_2))$. Moreover, from the fact that $\SP (\stab(x_2))$ is
%   coarser than $\SP (\stab(x_1))$, it follows that there exists $P \in
%   \SP(\stab(x_2))$ such that $P_1 \subseteq P$. From the fact that
%   $\frac{n}{2} < \vert P_1 \vert \leq \vert P \vert$ and $P_2$ is the only
%   part such that $\frac{n}{2} < \vert P_2 \vert$, it follows that $P_1
%   \subseteq P = P_2$ and so $\consp(x_2) = [n] - P_2 \subseteq [n] - P_1 =
%   \consp(x_1)$.
% \end{proof}

\section{Support Theorems}
In this section we develop an analogous theorem to the support theorem of
Anderson and Dawar \cite{AndersonD17}.
%
%\begin{lem}[Support Lemma]
%  For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and
%  $n \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
%  structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
%  2^{n^{1-\epsilon}}$, then, for all $g \in C$, $\vert \SP (g) \vert \leq
%  \frac{n}{2}$.
% \end{lem}

% \begin{thm}[Support Theorem]
%   For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and
%   $n \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
%   structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
%   2^{n^{1-\epsilon}}$, then, $SP(C) \leq \frac{33}{\epsilon}\frac{\log s}{\log
%   n}$.
% \end{thm}

% \begin{lem}
%   For any $\epsilon$ and $n$ such that $\frac{2}{3} \leq \epsilon \leq 1$ and
%   $n \geq \frac{128}{\epsilon^2}$, if $C$ is a symmetric, rigid circuit on
%   structures of size $n$ and $s := \max_{g \in C} \vert \orb (g)\vert \leq
%   2^{n^{1-\epsilon}}$, then, for all $g \in C$, we have for all $(i,j) \in
%   \dom (L_g)$ that $\consp(i) \subseteq \consp (L_g(i,j))$ and $\consp(j)
%   \subseteq \consp(L_g (i,j)))$.
% \end{lem}

% \begin{lem}
%   Let $\mathcal{P}_1$ and $\mathcal{P}_2$ be partitions of $[n]$ such that
%   $\mathcal{P}_1 = A \cup S_1$ and $\mathcal{P}_2 = B \cup S_2$, and
%   \begin{enumerate}
%   \item for all $X \in A$ and $Y \in B$ we have that $X \cap Y = \emptyset$,
%     and
%   \item for all $x \in S_1 \cup S_2$, x is a singleton.
%   \end{enumerate}
%   It follows that $\varepsilon(\mathcal{P}_1, \mathcal{P}_2) = A \cup B \cup
%   S$, where $S$ is a set of singletons.
% \end{lem}
% \begin{proof}
% \end{proof}

% \begin{lem}
%   Let $G_1$ and $G_2$ be subgroups of $\sym_n$. Then $\SP^S(G_1) = \SP^S(G_2)$
%   iff $\consp^S(G_1) = \consp^S(G_2)$.
% \end{lem}
% \begin{proof}

% \end{proof}

% \begin{lem}
%   Let $G_1$ and $G_2$ be subgroups of $\sym_n$. Then $\consp^S(G_1) =
%   \consp^S(G_2)$ implies that $\consp (G_1) = \consp (G_2)$.
% \end{lem}
% \begin{proof}
% \end{proof}

% The following lemma asserts a few basic facts about the canonical row and
% column supports.

% \begin{lem}
%   Let $h \in H$, then $r_h \subset \consp(h)$, $c_h \subset \consp(h)$ and
%   $c_r \cup r_h = \consp(h)$.
% \end{lem}

\begin{definition}
  Let $\omega$ be a matrix labeling for $g$. Define the matrix stabilizer for
  $\omega$, denoted by $\matstab(\omega)$, to be the set of all $\sigma \in
  \sym_n$ such that $\sigma H = H$ and there exists $(\alpha, \beta) \in \sym_A
  \times \sym_B$ such that for all $(i,j) \in A \times B$ we have that $\omega
  (\alpha i, \beta j) = \sigma \omega (i,j)$.
\end{definition}

\begin{definition}
  Let $g$ be a gate with matrix labeling $\omega$, $h,h' \in H$ and $\sigma \in
  \sym_n$. We say that a pair $(h, h')$ is compatible with $(\sigma, \omega)$ if
  $\sigma h, \sigma h' \in H$ and there exists $(\gamma_1, \gamma_2),
  (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$ s.t.
  \begin{align*}
    &(\gamma_1, \gamma_2) \cdot \omega^{-1} (h) = \omega^{-1}(\sigma h), \text{ and} \\ 
    &(\gamma_1', \gamma_2') \cdot \omega^{-1} (h') = \omega^{-1}(\sigma h'),
  \end{align*}
  and for all $(i,j) \in \omega^{-1}(h)$, $(i',j') \in \omega^{-1}(h')$ we have
  that
  \begin{align*}
    &i =i' \implies \gamma_1(i) = \gamma_1'(i'), \text{ and} \\
    &j =j' \implies \gamma_2(j) = \gamma_2'(j').
  \end{align*}

\end{definition}

\begin{lem}
  Let $g$ be a gate, $\omega$ be a matrix labeling of $g$, $\sigma \in \sym_n$.
  Then $\sigma \in \matstab(\omega)$ iff for all $h,h' \in H$ we have that
  $(h,h')$ is compatible with $(\sigma, \omega)$.
\end{lem}

\begin{proof}
  $`\Rightarrow'$: We have that $\sigma \in \matstab(\omega)$ and so there
  exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that for all $(i,j) \in
  A \times B$ we have $\sigma \omega (i,j) = \omega (\alpha i, \beta j)$. From
  compatibility we have that $h,h' \in H$ Let $h, h' \in H$ . Let $(\gamma_1,
  \gamma_2) := (\gamma_1', \gamma_2') := (\alpha, \beta)$. This assignment is
  sufficient to prove the direction.

  $`\Leftarrow'$: Suppose for all $h,h' \in H$ we have $(\gamma_1, \gamma_2),
  (\gamma_1, \gamma_2') \in \sym_A \times \sym_B$ satisfying the above
  requirements. Notice that for a given $i \in A$ and any $j, j' \in B$, let $h
  = \omega(i,j)$ and $h' = \omega(i,j')$, then we have that $\gamma_1 (i) =
  \gamma_1'(i)$. It follows that we can define a $\alpha \in \sym_A$ by
  $\alpha(i) = \gamma_1 (i)$. Similarly we can define $\beta \in \sym_B$ by
  $\beta (j) = \gamma_2 (j)$.

\end{proof}

\begin{definition}
  Let $g$ be a gate with matrix labeling $\omega$. Let $(\sigma, h, h') \in
  \sym([n]) \times H^2$. Say that $(\sigma, h, h')$ is useful if $(h,h')$ is
  incompatible with $(\sigma, \omega)$.

  Say that two distinct pairs $(\sigma_1, h_1, h_1'), (\sigma_2, h_2, h_2') \in
  \sym_n\times H^2$ are mutually independent if
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $\sigma_2 h_1 = h_1$,
  \item $\sigma_2 \sigma_1 h_1 = \sigma_1 h_1$,
  \item $\sigma_2 h_1' = h_1'$,
  \item $\sigma_2 \sigma_1 h_1' = \sigma h_1'$,
  \end{itemize}
  We say that a set $S \subseteq \sym_n \times H^2$ is useful if each pair in
  it is useful. We say that S is independent if each pair of distinct pairs in
  $S$ are mutually independent.
\end{definition}

We denote the usual equivalence relation on $\sym_n$ from the (right) cosets of
$\matstab(\omega)$ by $\sim_\omega$.

\begin{lem}
  Let $\sigma_1, \sigma_1 \in \sym_n$ and suppose $\sigma_1 \sim_\omega
  \sigma_2$ then for any $(h,h') \in H^2$ we have that $(h,h')$ is compatible
  with $(\sigma_1, \omega)$ iff $(h,h')$ is compatible with $(\sigma_2,
  \omega)$.
\end{lem}

\begin{proof}
  Suppose we have that $\sigma_1 \sim_\omega \sigma_2$. And additionally
  supposed $(h, h')$ compatible with $(\sigma_1, \omega)$.

  It follows there exists $(\alpha, \beta) \in \sym_A \times \sym_B$ such that
  $\sigma_1 \omega (i,j) = \sigma_2\omega (\alpha i, \beta j)$, and we have
  $(\gamma_1, \gamma_2), (\gamma_1', \gamma_2') \in \sym_A \times \sym_B$
  satisfying the requirements of compatibility. We note that $(\alpha, \beta)
  \cdot \omega^{-1}(\sigma_1 h) = \omega^{-1}(\sigma_2 h)$. Thus by composition
  we have that $(\alpha \gamma_1, \beta \gamma_2) \cdot \omega^{-1}(h) =
  \omega^{-1}(\sigma_2 h)$ and $(\alpha \gamma_1', \beta \gamma_2') \cdot
  \omega^{-1}(h') = \omega^{-1}(\sigma_2 h')$, and clearly the remaining
  requirement for compatibility follows from the bijectivity of $\alpha$ and
  $\beta$. The result follows. The other direction of the implication follows
  from symmetry.
\end{proof}

\begin{claim}
  \label{claim:useful-independant-set}
  Let $g$ be a rank gate with labeling $\omega$ and child set $H$. Let $S$ be a
  useful and independent. We then have that $\vert \sym_n: \matstab(\omega)
  \vert \leq 2^{\vert S \vert}$.
\end{claim}

\begin{proof}
  Let $R \subseteq S$ and define $\sigma_R = \Pi_{(\sigma, h, h') \in R} \sigma$
  (with some arbitrary order assumed on $S$). Let $R$ and $Q$ be distinct
  subsets of $S$ and WLOG let $\vert R \vert \geq \vert Q \vert$. We want to
  show that we don't have $\sigma_R \omega \sim_\omega \sigma_Q \omega$. Pick
  any $(\sigma, h, h') \in R/Q \neq \emptyset$. Given that $\sigma_R h = \sigma
  h$ and $\sigma_R h' = \sigma h'$ it is easy to see that the usefulness of
  $(\sigma, h,h')$ implies the incompatibility of $(h,h')$ with with $(\omega,
  \sigma_R)$. Moreover, the fact that $\sigma_Q h = h$ and $\sigma_Q h' = h'$
  makes it easy to see $(h,h')$ is compatible with $(\omega, \sigma_Q)$. From
  the above lemma we may conclude that that we do not have $\sigma_R \sim_\omega
  \sigma_Q$, and the result follows.
\end{proof}

The following two lemmas proved by Anderson and Dawar \cite{AndersonD17} are
both of use in proving the following theorem.

>>>>

\documentclass[../paper.tex]{subfiles}

\begin{document}
Symmetric circuits, as developed by Anderson and Dawar, are, importantly defined
over (complete) Boolean basis consisting of symmetric functions. The following
result shows that once a majority gate has been included in this basis any
symmetric function can be computed using polynomial-size symmetric circuits, and
as such no additional symmetric function added to the Basis improves the power
of the model.

@@

\subsection{G-Symmetric Functions}
In order to extend the notion of a circuit by extending the basis we need to
consider functions that are not symmetric in the full sense of the term but have
some weakened notion of symmetry.

@@

@@

% In this section I discuss how to determine the rank a matrix labelling at some
% gate $g$. This is a rough copy written for the purpose of discussion. In this
% section we fix some circuit $C_n$ and some rank gate $g$ in $C_n$ with a set
% of children $H$ and matrix labelling $L: [a] \times [b] \rightarrow H$ (which
% we assume WLOG is a bijection).
\end{document}
